\documentclass[12pt]{article}

\usepackage[NoDate]{currvita}
\usepackage[letterpaper, margin=0in]{geometry}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}

\renewcommand{\cvheadingfont}{\rmfamily\bfseries\Huge}
\renewcommand{\cvlistheadingfont}{\rmfamily\scshape\Large}
\renewcommand{\familydefault}{\sfdefault}
\hypersetup{colorlinks,urlcolor=Crimson}

\addtolength{\hoffset}{0in}
\addtolength{\voffset}{0.125in}

\setsansfont{Roboto}[
    Path=./fonts/Roboto/,
    Extension = .ttf,
    UprightFont=*-Light,
    BoldFont=*-Bold,
    ItalicFont=*-Italic,
    BoldItalicFont=*-BoldItalic
  ]

\setromanfont{Montserrat}[
    Path=./fonts/Montserrat/,
    Extension = .ttf,
    UprightFont=*-Thin,
    BoldFont=*-Light,
    ItalicFont=*-Italic,
    BoldItalicFont=*-BoldItalic
  ]

\begin{document}

  \centering
  \begin{cv}{Luis Alejandro Mart\'inez Faneyth}
    
    \vspace{0.25em}
    \href{mailto:luis@luisalejandro.org}{luis@luisalejandro.org} •
    \href{https://luisalejandro.org/portfolio}{luisalejandro.org/portfolio} •
    \href{https://github.com/LuisAlejandro}{github.com/LuisAlejandro}
    \vspace{0.125em}

    \hrulefill

    \begin{minipage}[t]{0.75\textwidth}
      \vspace{4em}

      \textrm{\textsc{\Large{Dear [Hiring Manager],}}}
      \vspace{2em}
      \newline
      \parbox[t]{\linewidth}{
        \linespread{1.5}\selectfont
          I've been taking a look at the products [Company] offers and I'm very interested in joining your team. As a software engineer with +13 years in the field, I've helped several latin american startups hit and exceed their development needs.
          \newline

          On 2022 I joined \href{https://wheeltheworld.com}{Wheel the World}, a startup that helps people with disabilities in organizing accessible travel. My first assignment was to integrate the company's website backend with the \href{https://expedia.com}{expedia.com} shopping/booking API. My contributions were crucial to increase the company's revenue by 39\% on Q1 2023.
          \newline

          Earlier on 2020 I joined \href{https://soleit.app/es/inicio}{Soleit}, a startup specialized in designing foot insoles. I lead a team that developed a groundbreaking desktop app that allowed them to enter the growth stage, with financing from Ganesha Lab, UC Davis and others.
          \newline

          I've also worked with startups on Spain, Canada, Uruguay and Venezuela. We can discuss my experience in more detail during an interview.
          \newline

          Thank you for considering my application. I am excited about the opportunity to join [Company] and contribute to its success. Please don't hesitate to contact me if you have any questions.
          \newline

          Sincerely,
      }
      \vspace{0.125em}
      \parbox[t]{\linewidth}{
        \centering
        \vspace{4em}
        Luis Alejandro Mart\'inez Faneyth • \href{mailto:luis@luisalejandro.org}{luis@luisalejandro.org}
      }
    \end{minipage}

  \end{cv}
\end{document}
