\documentclass[12pt]{article}

\usepackage[NoDate]{currvita}
\usepackage[letterpaper, margin=0in]{geometry}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage[svgnames]{xcolor}

\renewcommand{\cvheadingfont}{\rmfamily\bfseries\Huge}
\renewcommand{\cvlistheadingfont}{\rmfamily\scshape\Large}
\renewcommand{\familydefault}{\sfdefault}
\hypersetup{colorlinks,urlcolor=Crimson}

\addtolength{\hoffset}{0in}
\addtolength{\voffset}{0.125in}

\setsansfont{Roboto}[
    Path=./fonts/Roboto/,
    Extension = .ttf,
    UprightFont=*-Light,
    BoldFont=*-Bold,
    ItalicFont=*-Italic,
    BoldItalicFont=*-BoldItalic
  ]

\setromanfont{Montserrat}[
    Path=./fonts/Montserrat/,
    Extension = .ttf,
    UprightFont=*-Thin,
    BoldFont=*-Light,
    ItalicFont=*-Italic,
    BoldItalicFont=*-BoldItalic
  ]

\begin{document}

\centering
\begin{cv}{Luis Mart\'inez}
  
  \vspace{0.25em}
  \textcolor{gray}{Telecom Engineer} •
  \textcolor{gray}{Software Engineer} •
  \textcolor{gray}{DevOps}

  \vspace{0.125em}
  \href{mailto:luis@luisalejandro.org}{luis@luisalejandro.org} •
  \href{https://luisalejandro.org/portfolio}{luisalejandro.org/portfolio}
  \vspace{0.125em}

  \hrulefill

  \begin{minipage}[t]{0.35\textwidth}
    \vspace{0.125em}
    
    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Education}}}
      \newline
      \parbox[t]{\linewidth}{
        \textbf{UNEFA} • \textrm{\textbf{Telecom Engineer}}\\
        2009 • Maracay, Venezuela\\
        \footnotesize{\textcolor{gray}{Design, development, implementation and debugging of electrical communications systems, electronic, electromagnetic or optical.}}\\
      }
      \newline
      \parbox[t]{\linewidth}{
        \textbf{CNTI} • \textrm{\textbf{Advanced python}}\\
        2011 • Caracas, Venezuela\\
        \footnotesize{\textcolor{gray}{Structures, virtual environments, version control systems, reStructuredText, Sphinx, Django, Sqlite, GUI (pyGTK, pyQT), iterators, generators, decorators, unit tests.}}\\
      }
      \newline
      \parbox[t]{\linewidth}{
        \textbf{CNTI} • \textrm{\textbf{Basic python}}\\
        2011 • Caracas, Venezuela\\
        \footnotesize{\textcolor{gray}{Interpreter, standard library, basic functions, data types, modules, cycles, interaction with the user and the operating system, output format, error handling.}}\\
      }
      \newline
    \end{minipage}

    \vspace{0.25em}
    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Skills}}}
      \newline
      \parbox[t]{\linewidth}{
        \textbf{Languages} • \footnotesize{\textcolor{gray}{Spanish (native), English (fluent)}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Programming} • \footnotesize{\textcolor{gray}{Node, Python, Golang, PHP, Shell script, Make.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Frontend} • \footnotesize{\textcolor{gray}{Ionic, React, NextJS, Jekyll, Django, Flask.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Backend} • \footnotesize{\textcolor{gray}{NestJS, Express, TypeORM, Firebase, Elastic, MySQL, MongoDB, Redis.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{DevOps} • \footnotesize{\textcolor{gray}{Docker, Kubernetes, Git, AWS, GCP, Github Actions, Ansible.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Diagramming} • \footnotesize{\textcolor{gray}{Markdown, reStructuredText, \LaTeX.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Other} • \footnotesize{\textcolor{gray}{Debian packaging, custom kernels and installable ISO images for GNU/Linux distributions. Python Packaging.}}
      }
      \newline
      \newline
    \end{minipage}

    \vspace{0.25em}
    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Conferences}}}
      \newline
      \parbox[t]{\linewidth}{
        \textbf{Debian Day} • \textrm{\textbf{Speaker}}\\
        2018 • Maracay, Venezuela\\
        \footnotesize{\textcolor{gray}{The Internal World of a Programmer.}}\\
      }
      \newline
      \parbox[t]{\linewidth}{
        \textbf{DebConf 2012} • \textrm{\textbf{Speaker/Developer}}\\
        2012 • Managua, Nicaragua\\
        \footnotesize{\textcolor{gray}{Making derivative distributions with Canaima Semilla.}}\\
      }
      \newline
    \end{minipage}

    \vspace{0.25em}
    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Side projects}}}
      \newline
      \parbox[t]{\linewidth}{
        \textbf{Dockershelf} • \href{https://github.com/Dockershelf/dockershelf}{Dockershelf/dockershelf}\\
      }
      \parbox[t]{\linewidth}{
        \textbf{Agoras} • \href{https://github.com/LuisAlejandro/agoras}{LuisAlejandro/agoras}\\
      }
      \parbox[t]{\linewidth}{
        \textbf{Spices} • \href{https://github.com/LuisAlejandro/spices}{LuisAlejandro/spices}\\
      }
    \end{minipage}
  
  \end{minipage}\hspace{0.5cm}
  \begin{minipage}[t]{0.55\textwidth}
    \vspace{0.125em}

    \textrm{\textsc{\Large{Experience}}}
    \newline
    \parbox[t]{\linewidth}{
      \textbf{\href{https://collagelabs.org}{Collage Labs}} • \textrm{\textbf{Founder}}\\
      Jan 2020 --- present • Maracay, Venezuela\\
      \footnotesize{\textcolor{gray}{Worked with project managers and developers supervising requirement completion for clients around the world. Worked with designers to set up website and social media presence. Identified and maximized sales opportunities resulting in 6 new clients.}}\\
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://wheeltheworld.com}{Wheel The World}} • \textrm{\textbf{Senior Software Engineer}}\\
      Jun 2022 --- Jul 2023 • Berkeley, United States (Remote)\\
      \footnotesize{\textcolor{gray}{Developed new CRUD modules to web applications based on Next.js and TypeORM. Automatized data loading operations using Golang. Developed the new CI/CD workflow of the company by using Docker, Google Cloud Run and Github Actions. Implemented the price and booking integration with expedia.com. Developed modules for a content management application based on October CMS (Laravel, PHP).}}\\
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://soleit.app}{Soleit}} • \textrm{\textbf{Full Stack Developer}}\\
      Oct 2020 --- Jun 2022 • Santiago, Chile (Remote)\\
      \footnotesize{\textcolor{gray}{Built the backend and frontend of SoleTech 2.0, a groundbreaking desktop app which allows to diagnose and design specialized foot insoles. Implemented an Electron container for an Ionic-React app. Used Express.js, Sequelize and Postgres to create a REST API. Its release allowed Soleit to enter the growth stage, with financing from Ganesha Lab, UC Davis and CORFO Chile.}}\\
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://guayoyo.io}{Guayoyo}} • \textrm{\textbf{Python Developer}}\\
      Jun 2019 --- Dec 2021 • Montevideo, Uruguay (Remote)\\
      \footnotesize{\textcolor{gray}{Implemented speed and memory optimizations to \href{https://howlermonkey.io}{HowlerMonkey} updater, which translated to a 66\% memory reduction and faster updates. Developed modules to add vulnerabilities sources to the index, including: OpenVAS, Nessus, Metasploit, ExploitDB, PacketStorm, Snort, Suricata and Nmap, allowing Guayoyo to add value, increase sales and reduce costs.}}\\
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://web.archive.org/web/20180413143616/https://webuzz.es/}{Webuzz}} • \textrm{\textbf{Wordpress Developer}}\\
      Apr 2019 --- Apr 2020 • Madrid, Spain (Remote)\\
      \footnotesize{\textcolor{gray}{Developed \href{https://web.archive.org/web/20201101021046/https://www.recetags.com/}{Recetags} and \href{https://web.archive.org/web/20191206145303/https://www.ginburdon.com/}{Gin Burdon} websites using Wordpress and AJAX technologies.}}\\
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://leadboxhq.com}{Leadbox}} • \textrm{\textbf{Full Stack Developer}}\\
      May 2018 --- Feb 2020 • Ottawa, Canada (Remote)\\
      \footnotesize{\textcolor{gray}{Implemented an asset build queue based on webpack and client-server architecture. Developed Marvin, a video creation app configurable by json files. Developed a deployment system for Wordpress sites using Ansible. Implemented UI/UX optimizations on Leaderboard, an Angular web app. Created Wordpress plugins. Developed \href{https://leadboxhq.com}{Leadbox homepage}.}}\\
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://guayoyo.io}{Guayoyo}} • \textrm{\textbf{Python Developer}}\\
      Jul 2017 --- May 2018 • Montevideo, Uruguay (Remote)\\
      \footnotesize{\textcolor{gray}{Created the backend for \href{https://howlermonkey.io}{HowlerMonkey}, a vulnerability reporting app. Implemented HowlerMonkey's REST API using Flask.}}\\
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://www.cnti.gob.ve}{CNTI}} • \textrm{\textbf{Linux Architect}}\\
      Nov 2009 --- Jul 2014 • Caracas, Venezuela\\
      \footnotesize{\textcolor{gray}{Developed versions 3.0, 3.1, 4.0 and 4.1 of Canaima GNU/Linux Operating system, allowing the venezuelan government to reduce costs of shipping 6 million laptops for educational program \textsl{Canaima Educativo}.}}\\
    }
  \end{minipage}

\end{cv}
\end{document}
