\documentclass[12pt]{article}

\usepackage[NoDate]{currvita}
\usepackage[letterpaper, margin=0in]{geometry}
\usepackage{hyperref}
\usepackage{fontspec}
\usepackage[svgnames]{xcolor}

\renewcommand{\cvheadingfont}{\rmfamily\bfseries\Huge}
\renewcommand{\cvlistheadingfont}{\rmfamily\scshape\Large}
\renewcommand{\familydefault}{\sfdefault}
\hypersetup{colorlinks,urlcolor=Crimson}

\addtolength{\hoffset}{0in}
\addtolength{\voffset}{0.125in}

\setsansfont{Roboto}[
    Path=./fonts/Roboto/,
    Extension = .ttf,
    UprightFont=*-Light,
    BoldFont=*-Bold,
    ItalicFont=*-Italic,
    BoldItalicFont=*-BoldItalic
  ]

\setromanfont{Montserrat}[
    Path=./fonts/Montserrat/,
    Extension = .ttf,
    UprightFont=*-Thin,
    BoldFont=*-Light,
    ItalicFont=*-Italic,
    BoldItalicFont=*-BoldItalic
  ]

\begin{document}

\centering
\begin{cv}{Luis Alejandro Mart\'inez}
  
  \vspace{0.25em}
  \textcolor{gray}{Senior Full Stack Developer} •
  \textcolor{gray}{DevOps} •
  \textcolor{gray}{Telecom Engineer}

  \vspace{0.125em}
  +584243524970 •
  \href{mailto:luis@luisalejandro.org}{luis@luisalejandro.org\footnotesize{$\nearrow$}} •
  \href{https://luisalejandro.org/portfolio}{Portfolio\footnotesize{$\nearrow$}} •
  \href{https://www.linkedin.com/in/martinezfaneyth/}{LinkedIn\footnotesize{$\nearrow$}}
  \vspace{0.125em}

  \hrulefill

  \begin{minipage}[t]{0.35\textwidth}
    \vspace{0.125em}

    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{About me}}}
      \newline
      \parbox[t]{\linewidth}{
        \footnotesize{\textcolor{gray}{I'm} \textcolor{black}{passionate} \textcolor{gray}{about finding out end-user needs and creating \textcolor{black}{beautiful interfaces} with sustainable architecture. I've been on the field for more than \textcolor{black}{13 years}, but I'm always fascinated by \textcolor{black}{new technology}, which I try to integrate into new projects as soon as possible.}}\\
        \footnotesize{\textcolor{gray}{I've worked in backend, frontend and devOps roles with startups from the US, Chile, Uruguay, Spain, Canada, Mexico, and Venezuela. I've been in \textcolor{black}{leadership roles}, and I also founded my own startup.}}\\
        \footnotesize{\textcolor{gray}{Having worked remotely for more than \textcolor{black}{9 years}, I have extensive experience in agile methodologies. I'm a team player, always looking to guide and mentor colleagues in need of assistance.}}\\
      }
      \newline
    \end{minipage}

    \vspace{0.25em}
    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Skills}}}
      \newline
      \parbox[t]{\linewidth}{
        \textbf{Languages} • \footnotesize{\textcolor{gray}{Spanish (\textcolor{black}{Native}), English (\textcolor{black}{C2 Proficient}).}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Programming} • \footnotesize{\textcolor{gray}{Python (\textcolor{black}{+10 years}), Javascript (\textcolor{black}{+10 years}), Node (\textcolor{black}{+5 years}), Typescript (\textcolor{black}{+5 years}), Golang (\textcolor{black}{+2 years}).}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Frontend} • \footnotesize{\textcolor{gray}{React (\textcolor{black}{+3 years}), Vue, Ionic, Electron, Next, Chakra UI, Tailwind, Material UI.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Backend} • \footnotesize{\textcolor{gray}{Express (\textcolor{black}{+3 years}), TypeORM, Sequelize, Firebase, Elastic, MySQL, MongoDB, Redis.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{DevOps} • \footnotesize{\textcolor{gray}{Docker (\textcolor{black}{+9 years}), Kubernetes, AWS, GCP, Github Actions.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Markup} • \footnotesize{\textcolor{gray}{Markdown, reStructuredText, \LaTeX.}}
      }
      \parbox[t]{\linewidth}{
        \textbf{Other} • \footnotesize{\textcolor{gray}{Debian packaging, custom kernels and installable ISO images for GNU/Linux distributions. Python Packaging.}}
      }
      \newline
      \newline
    \end{minipage}

    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Education}}}
      \newline
      \parbox[t]{\linewidth}{
        \textbf{UNEFA} • \textrm{\textbf{Telecom Engineer}}\\
        Jul 2003 --- Jul 2009 • Maracay, Venezuela\\
        \footnotesize{\textcolor{gray}{Design, development, implementation and debugging of electrical communications systems, electronic, electromagnetic or optical.}}\\
      }
      \newline
    \end{minipage}

    \vspace{0.25em}
    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Certifications}}}
      \newline
      \parbox[t]{\linewidth}{
        \href{https://www.hackerrank.com/certificates/bab8ecba39a0}{HackerRank React\footnotesize{$\nearrow$}} • Nov 2023\\
      }
      \parbox[t]{\linewidth}{
        \href{https://www.hackerrank.com/certificates/f6c3ad45aaa1}{HackerRank Node\footnotesize{$\nearrow$}} • Nov 2023\\
      }
      \parbox[t]{\linewidth}{
        \href{https://www.efset.org/cert/Nptkoz}{EF SET English C2\footnotesize{$\nearrow$}} • Nov 2023\\
      }
    \end{minipage}

    \vspace{0.25em}
    \begin{minipage}{\linewidth}
      \textrm{\textsc{\Large{Open source}}}
      \newline
      \parbox[t]{\linewidth}{
        \textbf{Dockershelf} • \href{https://github.com/Dockershelf/dockershelf}{Dockershelf/dockershelf\footnotesize{$\nearrow$}}\\
      }
      \parbox[t]{\linewidth}{
        \textbf{Agoras} • \href{https://github.com/LuisAlejandro/agoras}{LuisAlejandro/agoras\footnotesize{$\nearrow$}}\\
      }
    \end{minipage}
  
  \end{minipage}\hspace{0.5cm}
  \begin{minipage}[t]{0.55\textwidth}
    \vspace{0.125em}

    \textrm{\textsc{\Large{Experience}}}
    \newline
    \parbox[t]{\linewidth}{
      \textbf{Freelancer} • \textrm{\textbf{Backend Developer / DevOps}}\\
      Jul 2023 --- Nov 2023 • Maracay, Venezuela\\
      \footnotesize{
        \vspace{-\topsep}
        \vspace{-\topsep}
        \begin{itemize}
          \setlength{\parskip}{0pt}
          \setlength{\itemsep}{0pt}
          \item \textcolor{gray}{Dockerized Django applications for clients at Upwork.}
          \item \textcolor{gray}{Deployed AWS Lambda functions in Python for clients at Upwork.}
          \item \textcolor{gray}{Developed Agoras and Agoras Actions, an open source library written in Python for publishing posts on social networks.}
          \item \textcolor{gray}{Created my portfolio (\href{https://luisalejandro.org/portfolio}{luisalejandro.org/portfolio\footnotesize{$\nearrow$}}) which is made with React and Next.}
        \end{itemize}
      }
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://wheeltheworld.com}{Wheel The World\footnotesize{$\nearrow$}}} • \textrm{\textbf{Senior Software Engineer}}\\
      Jun 2022 --- Jul 2023 • Berkeley, United States (Remote)\\
      \footnotesize{
        \vspace{-\topsep}
        \vspace{-\topsep}
        \begin{itemize}
          \setlength{\parskip}{0pt}
          \setlength{\itemsep}{0pt}
          \item \textcolor{gray}{Implemented the price and booking integration with Expedia. Used React, Next and Chakra UI to create reusable interfaces and components: the price list, the hotel details and the payment modules.}
          \item \textcolor{gray}{Developed new CRUD modules to web applications based on Node, Next and TypeORM.}
          \item \textcolor{gray}{Developed the new CI/CD workflow of the company by using Docker, Google Cloud Run and Github Actions.}
        \end{itemize}
      }
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://collagelabs.org}{Collage Labs\footnotesize{$\nearrow$}}} • \textrm{\textbf{Founder}}\\
      Jan 2020 --- Jan 2023 • Maracay, Venezuela\\
      \footnotesize{
        \vspace{-\topsep}
        \vspace{-\topsep}
        \begin{itemize}
          \setlength{\parskip}{0pt}
          \setlength{\itemsep}{0pt}
          \item \textcolor{gray}{Created a Bitcoin News site in Django. It consulted several Bitcoin news sites and saved copies to be paraphrased later by editors.}
          \item \textcolor{gray}{Worked with project managers and developers supervising requirement completion for clients around the world.}
          \item \textcolor{gray}{My team worked with React, Ionic, Chakra and Next for the frontend and Django in the backend. I lead the scrum meetings and presented demos to the clients.}
        \end{itemize}
      }
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://soleit.app}{Soleit\footnotesize{$\nearrow$}}} • \textrm{\textbf{Full Stack Developer}}\\
      Oct 2020 --- Jun 2022 • Santiago, Chile (Remote)\\
      \footnotesize{
        \vspace{-\topsep}
        \vspace{-\topsep}
        \begin{itemize}
          \setlength{\parskip}{0pt}
          \setlength{\itemsep}{0pt}
          \item \textcolor{gray}{Implemented an Electron container for an Ionic-React app. Used React and Material UI for the interface.}
          \item \textcolor{gray}{Created a Python driver for a foot hardware scanner and a Flask API to read and capture foot impressions.}
          \item \textcolor{gray}{Built the backend and frontend of SoleTech 2.0, a groundbreaking desktop app which allows to diagnose and design specialized foot insoles.}
          \item \textcolor{gray}{Used Node, Express, Sequelize and Postgres to create a REST API. Used AWS Lambda and S3 storage for the deployment.}
          \item \textcolor{gray}{Its release allowed Soleit to enter the growth stage, with financing from Ganesha Lab, UC Davis and CORFO Chile.}
        \end{itemize}
      }
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://guayoyo.io}{Guayoyo\footnotesize{$\nearrow$}}} • \textrm{\textbf{Backend Developer}}\\
      Jun 2019 --- Dec 2021 • Montevideo, Uruguay (Remote)\\
      \footnotesize{
        \vspace{-\topsep}
        \vspace{-\topsep}
        \begin{itemize}
          \setlength{\parskip}{0pt}
          \setlength{\itemsep}{0pt}
          \item \textcolor{gray}{Implemented speed and memory optimizations to \href{https://howlermonkey.io}{HowlerMonkey\footnotesize{$\nearrow$}} updater, which translated to a 66\% memory reduction and faster updates.}
          \item \textcolor{gray}{Developed modules to add vulnerabilities sources to the index, including: OpenVAS, Nessus and Nmap, allowing Guayoyo to add value, increase sales and reduce costs.}
        \end{itemize}
      }
    }\vspace{0.125em}
    \parbox[t]{\linewidth}{
      \textbf{\href{https://leadboxhq.com}{Leadbox\footnotesize{$\nearrow$}}} • \textrm{\textbf{Full Stack Developer}}\\
      May 2018 --- Feb 2020 • Ottawa, Canada (Remote)\\
      \footnotesize{
        \vspace{-\topsep}
        \vspace{-\topsep}
        \begin{itemize}
          \setlength{\parskip}{0pt}
          \setlength{\itemsep}{0pt}
          \item \textcolor{gray}{Implemented an asset build queue based on Node, Webpack and client-server architecture.}
          \item \textcolor{gray}{Developed Marvin, a video creation app configurable by JSON files, written in Python.}
          \item \textcolor{gray}{Developed a deployment system for Wordpress sites using Ansible.}
          \item \textcolor{gray}{Created Wordpress plugins. Developed \href{https://leadboxhq.com}{Leadbox homepage\footnotesize{$\nearrow$}}.}
        \end{itemize}
      }
    }
  \end{minipage}

\end{cv}
\end{document}
